An introduction to Docker for reproducible research, with examples from the R environment

### 2014-09-30 docker-paper/manuscript.Rmd
updating to reflect rocker work, etc

---
title: "An introduction to Docker for reproducible research, with examples from the R environment"
author: 
  - name: Carl Boettiger
    affiliation: 
      l1: Center for Stock Assessment Research, 
      l2: 110 Shaffer Rd, Santa Cruz, CA 95050, USA 
    email: cboettig(at)gmail.com
    footnote: Corresponding author
address: 
  - code: cstar
    address: | 
      Center for Stock Assessment Research,
      110 Shaffer Rd,
      Santa Cruz, CA 95050, USA 
abstract: |
  As computational work becomes more and more integral to many aspects of
  scientific research, computational reproducibility has become an issue
  of increasing importance to computer systems researchers and domain
  scientists alike. Though computational reproducibility seems more
  straight forward than replicating physical experiments, the complex
  and rapidly changing nature of computer environments makes being able
  to reproduce and extend such work a serious challenge.  In this paper,
  I explore common reasons that code developed for one research project
  cannot be successfully executed or extended by subsequent researchers.
  I review current approaches to these issues, including virtual machines
  and workflow systems, and their limitations. I then examine how the
  popular emerging technology Docker combines several areas from systems
  research - such as operating system virtualization, cross-platform
  portability, modular re-usable elements, versioning, and a 'DevOps'
  philosophy, to address these challenges.  I illustrate this with several
  examples of Docker use with a focus on the R statistical environment.

>>>>

---
title: "An introduction to Docker for reproducible research, with examples from the R environment"
author: 
  - name: Carl Boettiger
    affiliation:
      l1: Center for Stock Assessment Research, 
      l2: 110 Shaffer Rd, Santa Cruz, CA 95050, USA 
    email: cboettig(at)gmail.com
    footnote: Corresponding author
abstract: |
  As computational work becomes more and more integral to many aspects of
  scientific research, computational reproducibility has become an issue
  of increasing importance to computer systems researchers and domain
  scientists alike. Though computational reproducibility seems more
  straight forward than replicating physical experiments, the complex
  and rapidly changing nature of computer environments makes being able
  to reproduce and extend such work a serious challenge.  In this paper,
  I explore common reasons that code developed for one research project
  cannot be successfully executed or extended by subsequent researchers.
  I review current approaches to these issues, including virtual machines
  and workflow systems, and their limitations. I then examine how the
  popular emerging technology Docker combines several areas from systems
  research - such as operating system virtualization, cross-platform
  portability, modular re-usable elements, versioning, and a 'DevOps'
  philosophy, to address these challenges.  I illustrate this with several
  examples of Docker use with a focus on the R statistical environment.
